TBD

### 2020-11-05 Articles/2020-ClassicalMechanicsPhil/Source/classical-phil-article.tex
Fixing some math notation

In our case, this applies to both the state of the whole system and to the state of its parts. That is, given an initial state $s_0$ there will be one and only one evolution $s(t)$ such that $s(t_0) = t_0$ [is $s$ an evolution that transports the state variables, i.e. labeling future states by the original state variables so that the initial time is transported to itself? I think we need to explain more about how evolutions are defined]. Moreover, if $\rho(s(t_0), t_0)$ is the density associated to the initial particle [what exactly does `initial particle' mean? Do we mean the initial state of the composite system or just a particular particle?] at the initial time, we must have that $\rho(s(t), t) = \rho(s(t_0), t_0)$, i.e. the density remains the same throughout the evolution. In other words, all particles that begin in a given initial state must end up in the same final state and vice-versa [could two different particles occupy the same initial state?].

@@

If we look at the whole distribution, we have $\rho(q^i, p_j) = |J| \rho(x^i, v^j) = \left|\frac{\partial v^i}{\partial p_j}\right| \rho(x^i, v^j)$ since
\begin{equation}
|J| = \begin{bmatrix}
\frac{\partial x^i}{\partial q^j} & \frac{\partial v^i}{\partial q^j} \\
\frac{\partial x^i}{\partial p_j} & \frac{\partial v^i}{\partial p_j}
\end{bmatrix}
= \begin{bmatrix}
\delta^i_j & \frac{\partial v^i}{\partial q^j} \\
0 & \frac{\partial v^i}{\partial p_j}
\end{bmatrix}
= \left|\frac{\partial v^i}{\partial p_j}\right|.
\end{equation}
Note that while the value given by $\rho(q^i, p_j)$ is coordinate independent, the value given by $\rho(x^i, v^j)$ depends on the choice of coordinate through $\left|\frac{\partial v^i}{\partial p_j}\right|$. If $x^i$ truly sets the unit system by itself, then $\left|\frac{\partial v^i}{\partial p_j}\right|$ must be a function of position only. Similar considerations will also hold for marginal distributions (i.e. distributions on a subset of the coordinates) which means all components of $\frac{\partial v^i}{\partial p_j}$ must be a function of position only. We set:
\begin{equation}
\begin{aligned}
\frac{\partial v^i}{\partial p_j} = \frac{1}{m} g^{ij} \\
\frac{\partial p_j}{\partial v^i} = m g_{ji}
\end{aligned}
\end{equation}
where $m$ is the unit conversion constant between velocity and conjugate momentum while $g_{ij}$ represents the linear dependency.

>>>>

In our case, this applies to both the state of the whole system and to the state of its parts. Let $\lambda : \mathbb{R} \to \mathcal{S}$ be the evolution over time of the state of a particle. Under the assumption, this will be uniquely identified by the initial state $s_0 = \lambda(t_0)$ at the initial time $t_0$. [is $s$ an evolution that transports the state variables, i.e. labeling future states by the original state variables so that the initial time is transported to itself? I think we need to explain more about how evolutions are defined]. Moreover, if $\rho(\lambda(t_0), t_0)$ is the density associated to the initial particle [what exactly does `initial particle' mean? Do we mean the initial state of the composite system or just a particular particle?] at the initial time, we must have that $\rho(\lambda(t), t) = \rho(\lambda(t_0), t_0)$, i.e. the density remains the same throughout the evolution. In other words, all particles that begin in a given initial state must end up in the same final state and vice-versa [could two different particles occupy the same initial state?].

@@

If we look at the whole distribution, we have $\rho(q^i, p_j) = |J| \rho(x^i, v^j) = \left|\frac{\partial v^i}{\partial p_j}\right| \rho(x^i, v^j)$ since
\begin{equation}
\begin{aligned}
|J| &= \begin{vmatrix}
\frac{\partial x^i}{\partial q^j} & \frac{\partial x^i}{\partial p_j} \\
\frac{\partial v^i}{\partial q^j} & \frac{\partial v^i}{\partial p_j}
\end{vmatrix}
= \begin{vmatrix}
\delta^i_j & 0 \\
\frac{\partial v^i}{\partial q^j} & \frac{\partial v^i}{\partial p_j}
\end{vmatrix} \\
&= \left|\delta^i_j\right| \left|\frac{\partial v^i}{\partial p_j}\right| - \left|0\right| \left|\frac{\partial v^i}{\partial q^j}\right|
= \left|\frac{\partial v^i}{\partial p_j}\right|.
\end{aligned}
\end{equation}
Note that while the value given by $\rho(q^i, p_j)$ is coordinate independent, the value given by $\rho(x^i, v^j)$ depends on the choice of coordinate through $\left|\frac{\partial v^i}{\partial p_j}\right|$. If $x^i$ truly sets the unit system by itself, then $\left|\frac{\partial v^i}{\partial p_j}\right|$ must be a function of position only. Similar considerations will also hold for marginal distributions (i.e. distributions on a subset of the coordinates) which means all components of $\frac{\partial v^i}{\partial p_j}$ must be a function of position only. We set:
\begin{equation}
\begin{aligned}
\frac{\partial v^i}{\partial p_j} = \frac{1}{m} g^{ij} \\
\frac{\partial p_j}{\partial v^i} = m g_{ji}
\end{aligned}
\end{equation}
where $m$ is the unit conversion constant between velocity and conjugate momentum while $g_{ij}$ represents the linear dependency.
